### 2024-06-25 correlation.qmd
20240625 - suppress message
20240625 - distance correlation

Correlation is a metric of the association between variables.
Covariance is the association between variables and in an unstandardized metric that differs for variables with different scales.
By contrast, correlation is in a standarized metric that does not differ for variables with different scales.
When examining the association between variables that are [interval](#sec-interval) or [ratio](#sec-ratio) levels of measurement, Pearson correlation is used.
When examining the association between variables that are [ordinal](#sec-ordinal) in level of measurement, Spearman correlation is used.
Pearson correlation is an index of the *linear* association between variables.
If a nonlinear association is present, other indices like xi [$\xi$; @Chatterjee2021] are better suited to detecting the association.

@@

dev.off() #par(mfrow = c(1,1))
```

>>>>

Correlation is a metric of the association between variables.
Covariance is the association between variables and in an unstandardized metric that differs for variables with different scales.
By contrast, correlation is in a standarized metric that does not differ for variables with different scales.
When examining the association between variables that are [interval](#sec-interval) or [ratio](#sec-ratio) levels of measurement, Pearson correlation is used.
When examining the association between variables that are [ordinal](#sec-ordinal) in level of measurement, Spearman correlation is used.
Pearson correlation is an index of the *linear* association between variables.
If a nonlinear association is present, other indices like xi [$\xi$; @Chatterjee2021] and distance correlation coefficients are better suited to detect the association.

@@

invisible(dev.off()) #par(mfrow = c(1,1))
```
